-

### 2023-02-01 DRAFT_homogeneous_impact_areas.Rmd
bug: wrong path

```{r, include=F}
infra_agg_discrete_vect <- readRDS(paste0(path, "infra_agg_discrete_vect.rds"))
```

>>>>

```{r, include=F}
path <- ifelse(dir == "C:", 
        "P:/41201785_okologisk_tilstand_2022_2023/data/cache/",
        "/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/cache/")

infra_agg_discrete_vect <- readRDS(paste0(path, "infra_agg_discrete_vect.rds"))
```
